Group 9 Paper

### 2021-12-16 paper.Rmd
more rep tree

In the paper Banerjee, et al. discuss how to choose the most representative tree in a n esemble.

>>>>

In the paper Banerjee, et al. discuss how to choose the most representative tree in an ensemble, which is done by finding the average distance between one tree and all other trees in the ensemble. Banerjee, et al. discusses several types of distance in this paper only one of them was used, as it was already implemented in R package. This measure captures the similarities between the predictions, in that 2 trees are similar if they have the same predictions outcomes
